---
title: "R_databasepackage_use"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---


#1.use R to connect database(RMySQL,RODBC)


you should require packages of RMySQL and RODBC  first
```{r,echo=TRUE,results="hide"}
library(RMySQL)
library(RODBC)
```


#2.RMySQL(warning:this is not suitable for chinese character(you can read the table including chinese character,but not write the table including chinese )


###(1)we use the function "dbConnect"" to connect the mysql database
```{r,echo=TRUE,results='markup'}
conn<-dbConnect(MySQL(),dbname="php_one",username="root",password="zhaolei19930410")
```

###(2)the function "dbListTable" show the tables of dbname that we connect above
```{r}
dbListTables(conn)
```

###(3)we can write data into database
```{r}
id<-1:10
name<-letters[1:10]
data<-rnorm(10)
dat<-data.frame(id=id,name=name,data=data)
dbWriteTable(conn,"test7",dat)
```
###(4)we can select data from tables that we write above
```{r,results='hide'}
dbSendQuery(conn,'SET NAMES gbk')   # this is for characters in R,it's important, otherwise,you will not see the correct answer
```
```{r,results='markup'}
res=dbSendQuery(conn,"select * from test7")
dat=fetch(res)
dat
dbDisconnect(conn)
```


#3.RODBC(this package is suitable for all databases,including mysql,sqlserver,oracle,ect)

###(1)first you should set the environment and dbname you use in this project(if you don't know how to do this,you can google it)

###(2)connect to the database that is set above

```{r}
con<-odbcConnect("mysql",uid="root",pwd="zhaolei19930410")
sqlTables(con)  #this function is used for showing tables in the danames above
```
###(3)we write table into database(it's avaiable for chinese character)

```{r}
a<-c(1:3)
b<-c("zh","赵","李")
dat2<-data.frame(a=a,b=b)
sqlSave(con,dat2,tablename="test8")
sqlQuery(con,"select * from test8")
sqlFetch(con,"test8")
odbcClose(con)
```







